Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives.\\ \bigskip Supplementary Material

### 2015-03-24 paper/Diversity_supplementary.tex
Added golden mole diagram to the supplementary, semilandmark subsampling for each skull view

\subsection{Landmark descriptions}
\vspace*{-0.5cm}
	The information below provides further details about the landmarks we used to summarise morphological shape in tenrec and golden mole skulls. Landmark numbers and curve descriptions refer to Figure 2 in the main paper. One of us (SF) placed all of the landmarks on each picture.

>>>>

\subsection{Landmark descriptions}
\vspace*{-0.5cm}
	The information below provides further details about the landmarks we used to summarise morphological shape in tenrec and golden mole skulls. Landmark numbers and curve descriptions refer to Figure 2 in the main paper (example of a tenrec skull) and also Figure S1 (example golden mole skull). One of us (SF) placed all of the landmarks on each picture.

	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light.png}
	\caption[]
		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view. See Tables S1, S2 and S3 for more detailed landmark descriptions. The skulls are an example of a \textit{Chlorotalpa duthieae} (Duthie's golden mole), museum accession number AMNH 161527.}
	\label{fig:gmole}
	\end{figure}
